Competition

### 2020-09-21 R/competition wrangling.Rmd
calculate number of plants within rings of different radii

```{r}
ha_test <-
  ha %>%
  filter(plot == first(plot)) %>%
  filter(year == first(year)) %>%
  filter(row_number <=3, column <=3) %>% 
  add_column(plant = 1) #just a dummy indicator column for use later
ha_test
```

@@

```{r}
#density between 0m and 10m away
dist_0_10 <-
  dist_full %>% 
  filter(dist >=0, dist <10) %>% 
  group_by(row_from, column_from) %>% 
  summarize(n_neighbors_0_10 = sum(n_plants, na.rm = TRUE),
            n_cells = n(),
            density_0_10 = n_neighbors_0_10/n_cells,
            shtsper_0_10 = sum(n_shts, na.rm = TRUE)/n())
```
So at [1,1] there are only 3 cells between 5 and 15m away, there are a total of 6 plants in those cells, so the conspecific density at that distance is 2.0 plants / 100m^2 or 3.66 shoots / 100m^2

@@

```{r}
dens_0_10 <-
  ha_dist %>% 
  filter(dist>=0 & dist <10) %>% 
  group_by(plot, year, row_from, column_from) %>% 
  summarize(density_0_10 = sum(n_shts, na.rm = TRUE)/n())
left_join(ha, dens_0_10, by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
```

@@

```{r}
width <- 10 #meters
max <- 100 #meters
L <- seq(0, max-width, by = width)
U <- seq(0 + width, max, by = width)

@@

>>>>

```{r}
ha_test <-
  ha %>%
  filter(plot == first(plot)) %>%
  filter(year == first(year)) %>%
  filter(row_number <= 3, column <= 3) %>% 
  add_column(plant = 1) #just a dummy indicator column for use later
ha_test
```

@@

```{r}
#density between 0m and 10m away
dist_0_10 <-
  dist_full %>% 
  filter(dist >= 0, dist < 10) %>% 
  group_by(row_from, column_from) %>% 
  summarize(n_neighbors_0_10 = sum(n_plants, na.rm = TRUE),
            n_cells = n(),
            density_0_10 = n_neighbors_0_10/n_cells,
            shtsper_0_10 = sum(n_shts, na.rm = TRUE)/n())
```
So at [1,1] there are only 3 cells between 5 and 15m away, there are a total of 6 plants in those cells, so the conspecific density at that distance is 2.0 plants / 100m^2 or 3.66 shoots / 100m^2

@@

```{r}
dens_0_10 <-
  ha_dist %>% 
  filter(dist>= 0 & dist < 10) %>% 
  group_by(plot, year, row_from, column_from) %>% 
  summarize(density_0_10 = sum(n_shts, na.rm = TRUE)/n())
left_join(ha, dens_0_10, by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
```

@@

```{r}
width <- 10 #meters
max <- 100 #meters
L <- seq(0, max - width, by = width)
U <- seq(0 + width, max, by = width)

@@

# Using exact x, y coords
```{r}
library(furrr)
plan(multisession)
```

For a subset of plants in 2009, exact x,y coords in the plot were taken.  Use these to estimate density.

```{r}
ha_xy <-
  ha_new %>% 
  filter(!is.na(x_09) & !is.na(y_09))
ha_xy
```
It looks like the x, y coords are *within* each grid cell (e.g. A1).  Need to offset them to get relative coords for entire plot.  I'll make A1 = 0,0

```{r}
ha_xy <-
  ha_xy %>% 
  mutate(x_adj = x_09 + ((column - 1) * 10),
         y_adj = y_09 + ((row_number - 1) * 10),
         .after = y_09)
```

```{r}
ha_xy_s <-
  ha_xy %>% 
  group_by(ha_id_number) %>% 
  summarize(x = mean(x_adj),
            y = mean(y_adj))
#down to 3,571--still too big to do dist(), I think?

test <- ha_xy_s %>% select(x, y) %>% as.matrix()
rownames(test) <- paste(test[,1], test[,2], sep = ",")
head(test)
dist(test[1:5,])

```
Might not be the best approach

```{r}
eu_dist <- function(p1, p2) {
  sqrt(sum((p1 - p2)^2))
}
x = c(0,0)
y = c(3,3)
eu_dist(x, y)
```

For every ha_id_number, find only plants within 0-10 m, sum the number of shoots.

```{r}
ha_xy %>% 
  group_by(ha_id_number) %>% 
  rowwise() %>% 
  filter(eu_dist(
    c(first(cur_data()$x_adj), first(cur_data()$y_adj)),
    c(x_adj, y_adj)) < 10)
```

Nope

Start with single plot

```{r}
y1p1 <- ha_xy %>% 
  filter(year == first(year),
         plot == first(plot))
y1p1
```

```{r}
add_density_cols <- function(df, L, U, by, verbose = FALSE) {

  eu_dist <- function(p1, p2) {
    sqrt(sum((p1 - p2)^2))
  }

  d <- seq(L, U, by = by)

  df_out <- 
    future_map_dfr(1:nrow(df), function(r) { #loop through rows/plants
      #get coordinates for that plant
      focal_plant <- t(df[r, c("x_adj", "y_adj")])

      #calculate distance to every other plant
      focal_df <-
        df %>%
        rowwise() %>%
        mutate(dist = eu_dist(focal_plant, c(x_adj, y_adj)))

      #get total number of shoots at every ring
      future_map2_dfc(lag(d)[-1], d[-1],
               ~ transmute(focal_df,
                           !!glue("shts_{.x}_{.y}") := shts * (dist > .x & dist <= .y))) %>%
        ungroup() %>% 
        summarize(across(everything(), ~sum(., na.rm = TRUE)))
    })

  df_out <- bind_cols(df, df_out) #join to original data
  return(df_out)
}
# tic()
# add_density_cols(y1p1, L = 0, U = 10, by = 5)
# toc()
```

If I want this to be in units of shoots/m^2, then I need to calculate the area of the donut:

$$
A = \pi(U^2 - L^2)
$$
But also, like, truncate that donut if it passes outside of the plot.  I don't know how to do that.

```{r}
tic()
ha_xy2 <-
  ha_xy %>% 
  group_by(plot, year) %>% 
  group_split() %>% 
  head() %>% #test with 6 df to see how long it will take.
  future_map(~{
      add_density_cols(.x, L = 0, U = 10, by = 5) 
    })
toc()

```

Uggggh only works for first plot???
